Hypercoercions and a Framework for Equivalence of Cast Calculi

### 2019-10-27 paper.tex
Fixing grammar issues.
change eval

\newcommand{\evalEqv}[2]{\ensuremath{eval_{\text{#1}} = eval_{\text{#2}}}}

@@

\begin{proposition}[$L$ Properties]\label{thm:L-LazyD-monoid}\ 
  \begin{enumerate}
  \item $L$ is an instance of the Lazy D ADT
  \item $L$ is a monoid
  \item $cast(T,l,T) = id(T)$
  \end{enumerate}
\end{proposition}
\begin{proof}
  Part (1) is straightforward because property (1) and (2) are 
  trivially true and because $appS$ effectively repeats property (3) - 
  (11).
  Part (2) is true because list is known to be a monoid.
  Part (3) follows immediately from the definition of $cast(T,l,T)$
\end{proof}

\begin{lemma}[$L$ is Correct wrt. \ineffCEKD]
  \label{lem:L-correct}
  \[
  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
  \]
\end{lemma}
\begin{proof}
  Immediately from
  Correctness of \effCEK{C} (Lemma~\ref{thm:SD-equiv}) and 
  Properties of $L$ (Proposition~\ref{thm:L-LazyD-monoid}).
\end{proof}

@@

\begin{theorem}[\effCEK{C} is Correct wrt. \ineffCEKD{}]
  \label{thm:surely-lazyD-correct}
  Suppose $C$ is a \lazyD{} Cast ADT.  If
  $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
  \text{\evalEqv{\effCEK{C}}{\ineffCEKD}}
  \]
\end{theorem}
\begin{proof}
	Immediately from 
	\evalEqv{\effCEK{C}}{\effCEK{L}} (Lemma~\ref{thm:surely-lazyD-eqv})
	and
	\evalEqv{\effCEK{L}}{\ineffCEKD} (Lemma~\ref{lem:L-correct})
\end{proof}

@@

\figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercions. 
Applying the identity cast for the 
dynamic type succeeds immediately. Otherwise, we firstly 
apply the middle, then apply the tail. We denote by $r \; >>= \; f$ to mean 
that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise, the result 
is the failure.
$ applyMiddle(v,\ell,m)$ and $applyTail(v,t)$ are straightforward.
In the definition of $applyMiddle(v,\ell,m)$, we generalize 
shallow-consistency to compare middles and values ($v \smile m$) in the 
obvious way.

>>>>

\newcommand{\evalEqv}[2]{
	\ensuremath{
		eval_{\text{#1}}(e) = o
		\;\text{if and only if}\;
		eval_{\text{#2}}(e) = o}

@@

\begin{proposition}[$L$ Properties]\label{thm:L-LazyD-monoid}\ 
  \begin{enumerate}
  \item $L$ is an instance of the Lazy D ADT
  \item $L$ is a monoid
  \item $cast(T,l,T) = id(T)$
  \end{enumerate}
\end{proposition}
\begin{proof}
  Part (1) is straightforward because property (1) and (2) are 
  trivially true and because $appS$ effectively repeats property (3) - 
  (11).
  Part (2) is true because lists are known to be a monoid with respect to append.
  Part (3) follows immediately from the definition of $cast(T,l,T)$
\end{proof}

\begin{lemma}[$L$ is Correct wrt. \ineffCEKD]
  \label{lem:L-correct}
  If $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
  \text{\evalEqv{\effCEK{L}}{\ineffCEKD}}
  \]
\end{lemma}
\begin{proof}
  Immediately from
  Correctness of \effCEK{C} (Lemma~\ref{thm:SD-equiv}) and 
  Properties of $L$ (Proposition~\ref{thm:L-LazyD-monoid}).
\end{proof}

@@

\begin{theorem}[\effCEK{C} is Correct wrt. \ineffCEKD{}]
  \label{thm:surely-lazyD-correct}
  Suppose $C$ is a \lazyD{} Cast ADT.  If
  $\judgetype{\emptyset}{e}{T}$ and $o : T$, then
  \[
  \evalEqv{\effCEK{C}}{\ineffCEKD}
%  \judgeSeval{C}{e}{o}
%  \;\text{if and only if}\;
%  \judgeDeval{e}{o}
  \]
\end{theorem}
\begin{proof}
	Immediately from 
	Equivalence of \lazyD{} Cast ADTs (Lemma~\ref{thm:surely-lazyD-eqv})
%	\evalEqv{\effCEK{C}}{\effCEK{L}} (Lemma~\ref{thm:surely-lazyD-eqv})
	and
	$L$ is Correct wrt. \ineffCEKD{} (Lemma~\ref{lem:L-correct})
%	\evalEqv{\effCEK{L}}{\ineffCEKD} (Lemma~\ref{lem:L-correct})
\end{proof}

@@

\figref{hc-applyCast} defines $applyCast(v,c)$ for \lazyD\ hypercoercions. 
Applying the identity cast for the 
dynamic type succeeds immediately. Otherwise, we firstly 
apply the middle, then apply the tail. We denote by $r \; >>= \; f$ to mean 
that if $r$ is $\rOOsucc{v}$, the result is $f(v)$, otherwise, the result 
is the failure. The functions
$ applyMiddle(v,\ell,m)$ and $applyTail(v,t)$ are straightforward.
In the definition of $applyMiddle(v,\ell,m)$, we generalize 
shallow-consistency to compare middles and values ($v \smile m$) in the 
obvious way. Likewise, $applyTail(v, t)$ interprets the tail to the appropriate
cast of $v$.
